Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-11-24 paper/answer_reviewers.tex

\bigskip

\textit{My main comment concerns the bias in the observation of S minus P times. The authors measure the observed lag time from the centroid of the cross-correlation function within the time window 2 seconds before and after the theoretical lag time if the tremor source was on the plate boundary (L330-335). I understand that such kind of constraint is sometimes useful for obtaining realistic solutions, but I am worried whether this constraint works for too strong bias that concentrates all tremor depths to the plate boundary depths. In other words, the S minus P time measurements should be free from theoretical time lags when discussing the spatial relationship between tremor and plate boundary. How about using the whole time window or focusing on the window around the maximum peak? In any case, the authors should check and show that these time window limitations do not strongly affect the results.}

\bigskip

You bring up a very important point regarding the potential of bias in our results and we have explored this in some detail.  We have rewritten our method to include an important detail that we left out of the text of the submitted version which we now explain on lines 263-275.  We have also sent figures to show more clearly the windows we analyze for the clustering relative to the theoretical time and our final observation.  The highest peak in the absolute value of the phase-weighted stacks of the cross correlation functions $S_i(\tau)$ within the defined window is the same as the highest peak between 3 and  8 seconds for every array / tremor grid  except for one (BH 5, -5) so using the theoretical S-P time as a guide to define the time window has very little or no effect on the final travel-time observation.

\smallskip

The width of the time window selected to compute the moment centroid may have an effect on the estimation of the depth of the tremor. To verify this, we varied the width of the time window and computed the corresponding variations of the depth of the tremor. We added this discussion in the text at lines 368-377.

@@

\textit{I have only one minor quibble: in lines 443 - 445 the authors state "The depth range of the tremor is larger than the depth range of the low-frequency earthquakes, but this may be due to the uncertainty of the determination of the tremor depth." As far as I can tell, the depth range of members of an LFE family was not measured by Chestler and Creager (2017). Their three models assume a planar structure. A recent JGR paper by Sammis and Bostock (2021) proposed that LFEs beneath Vancouver Island occur at the sites of granular jams in a flow channel between 0.5 and 1.5 kilometers thick. So, the assumption of a planar distribution of LFEs in a family may be premature.}

\bigskip

There are two papers by Chestler and Creager in 2017. We added the reference in the text. Here, we are considering the range over all LFE families of the distance between the location of the LFE family and the plate boundary, not the depth range of the source of the LFEs within a single LFE family. The LFE families are close to the plate boundary, but not exactly on a plane. We modified the text and we added the comparison with the thickness of the flow channel.

\textbf{Additional figures related to first comment from Reviewer 1}

\begin{figure}
\includegraphics[width=\linewidth]{figures/intervals/BS_-05_-05_stacks.eps}
\caption{Stack of the cross-correlation functions for the Big Skidder array for the 110 one-minute long time windows when tremor was detected in a 5 km by 5 km grid cell located 7 kilometers southwest of the array. Red line corresponds to the cross-correlation of the East-West component with the vertical component, and blue line corresponds to the cross-correlation of the North-South component with the vertical component. The solid black line corresponds to the final observed S-P time, the black dotted line is the theoretical SP time if the source is on the plate boundary, and the grey dashed lines are the intervals $\left[T_{min} ; T_{max}\right]$ where we look for a secondary peak. For all the remaining figures, the two letters abbreviation in the title corresponds to the name of the array, and the numbers in parenthesis indicate the distance from the array to the grid cell in the east direction and the north direction.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-05_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-05_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-05_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-10_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-10_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-10_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-10_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-10_010_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-15_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-15_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-15_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-15_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-15_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-15_010_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-20_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-20_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-20_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-20_010_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-25_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_-25_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_000_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_000_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_005_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_005_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_005_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_010_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_010_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_010_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BH_020_-20_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-05_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-05_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-10_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-10_-20_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-10_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-10_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-15_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-20_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-20_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-20_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-20_-20_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-20_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-20_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-25_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_-25_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_000_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_000_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/BS_000_010_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/DR_000_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/DR_005_005_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/DR_005_010_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/DR_005_020_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/DR_005_025_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/DR_010_010_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/DR_010_015_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/DR_010_020_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/GC_010_010_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/GC_010_015_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/PA_-05_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/PA_000_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-05_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-05_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-05_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-05_-20_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-05_-25_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-10_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-10_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-10_-15_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-10_-20_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_-15_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_000_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_000_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_005_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_005_000_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_010_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_010_-10_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

### 2021-11-24 paper/answer_reviewers.tex

\begin{figure}[H]
\includegraphics[width=\linewidth]{figures/intervals/TB_015_-05_stacks.eps}
\caption{See caption of Figure 1 for an explanation of this figure.}
\end{figure}

### 2021-11-24 paper/agujournaltemplate.tex
Ready to submit?

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. We only want to verify whether the waveform $S_{i j} (\tau)$ around the secondary peak matches well with the stack $S_i (\tau)$. We thus look for the maximum of the absolute value of the stack $S_i (\tau)$ between one second before and one second after the theoretical time lag between P- and S-wave arrival if the source was on the plate boundary. We call the time lag corresponding to this maximum $\tau_{max}$. Then for the cross-correlation between $S_{i j} (\tau)$ and $S_i (\tau)$, we keep only the values of lag times $\tau$ between one second before and one second after $\tau_{max}$. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value $S_{i j} (\tau_{max})$ to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

We did this analysis for grid cells located in a 50 km by 50 km area centered on each of the eight arrays. We thus consider up to 11 * 11 * 8 = 968 values of the time lag between the direct P-wave and S-wave. We assumed that the epicenter is at the center of the grid and determined the depth that satisfies that epicenter and the observed S-minus-P time. The velocity models are taken from the 3D velocity model from ~\citeA{MER_2020}. For each array, we looked for the closest grid point (in terms of latitude and longitude) in the 3D model by ~\citeA{MER_2020} and used the corresponding layered model of compressional and shear wave speeds to compute the tremor depth. We thus used 8 different 1D velocity models corresponding to the 8 arrays. This allows us to take into account the substantial variations of the Poisson's ratio in the East-West direction.

@@

To compute the depth, we select the EW or the NS component with the larger maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the time lag $\tau_{max}$ corresponding to the secondary peak obtained earlier. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor.To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064 km, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054 km. We did the same analysis for the eight arrays of the experiment and each of the tremor-location grid points. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

@@

In Table 1, we report the values of the median, the median absolute deviation (MAD), and the Qn estimator of scale for the difference between the depth of the tremor and the low-frequency earthquakes and the depth of the plate boundary, for the McCrory model and for the Preston model. Small negative values of the median correspond to tremor and low-frequency earthquakes located a little bit above the plate boundary. The depth range of the tremor (Qn = 1.3 km) is larger than the depth range of the low-frequency earthquake families from ~\citeA{CHE_2017_JGR,CHE_2017_G3} (Qn = 0.9 km). It is a also larger than the thickness of the flow channel where ~\citeA{SAM_2021} suggest that the LFEs are generated (0.5 to 1.5 km). However, this may be due to the uncertainty on the determination of the tremor depth. The tremor and low-frequency earthquakes are slightly closer to the plate boundary for the Preston model than for the McCrory model. This may be due because the P-wave velocity model of ~\citeA{PRE_2003} was used as the initial velocity model by ~\citeA{MER_2020} to compute the full P- and S-wave velocity model that we use to get tremor depth from S minus P times. The Preston P-wave velocity model was also used by ~\citeA{CHE_2017_JGR,CHE_2017_G3} to locate the low-frequency earthquake families. \\

@@

\acknowledgments
The authors would like to thank A. Ghosh for sharing his tremor catalog. We also would like to thank Charles Sammis and an anonymous reviewer whose reviews have helped improve the paper. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS website using network code XG, 2009-2011. Most of the figures were done using GMT ~\cite{WES_1991}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/timelags}.

>>>>

In the following, we are only interested in the value of the stacks for time lags close to the secondary peak, and not in the entire time window for which we have computed the cross-correlation. To determine which time window to look at, we compute the theoretical value of the time lag between the P- and S-wave arrivals if the source was located on the plate boundary. We then look for the timing $\tau_{k l}$ of the absolute value of the stack in a time window starting 1 second before and ending 1 second after the theoretical time lag. $k$ and $l$ take values between 1 and 3 depending on whether the method used for the stacking of the stations and the stacking of the time windows is a linear stack, a $n$th-root stack or a phase-weighted stack. We thus have 9 possible values for the timing of the secondary peak. We define $T_{min} = \min_{k = 1,2,3 ; l=1,2,3} \tau_{k l} - 1$ and $T_{max} = \max_{k = 1,2,3 ; l=1,2,3} \tau_{k l} + 1$, and we limit the rest of our analysis to the time window $\left[ T_{min} ; T_{max} \right]$. \\

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. We want to verify whether the waveform $S_{i j} (\tau)$ around the secondary peak matches well with the stack $S_i (\tau)$. We thus look for the maximum of the absolute value of the stack $S_i (\tau)$ between one second before and one second after the theoretical time lag between P- and S-wave arrival if the source was on the plate boundary. We call the time lag corresponding to this maximum $\tau_{max}$. Then for the cross-correlation between $S_{i j} (\tau)$ and $S_i (\tau)$, we keep only the values of lag times $\tau$ between one second before and one second after $\tau_{max}$. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value $S_{i j} (\tau_{max})$ to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

We did this analysis for grid cells located in a 50 km by 50 km area centered on each of the eight arrays. We thus consider up to 11 * 11 * 8 = 968 values of the time lag between the direct P-wave and S-wave. We assumed that the epicenter is at the center of the grid and determined the depth that satisfies that epicenter and the observed S-minus-P time. The velocity models are taken from the 3D velocity model from ~\citeA{MER_2020}. For each array, we looked for the closest grid point (in terms of latitude and longitude) in the 3D model by ~\citeA{MER_2020} and used the corresponding layered model of compressional and shear wave speeds to compute the tremor depth. We thus used 8 different 1D velocity models corresponding to the 8 arrays. This allows us to take into account the substantial variations of the Poisson's ratio in the East-West direction. \\

We verify that using the expected value of the time lag between P- and S-wave arrival if the source was located on the plate boundary does not introduce bias in the analysis. The highest peak in the absolute value of the phase-weighted stack of the cross-correlation functions $S_i(\tau)$ within our defined window $\left[ T_{min} ; T_{max} \right]$ is the same as the highest peak between 3 and 8 seconds for every array / tremor grid  except for one (the grid cell located about 7 km south-east of the Burnt Hill array) so using the theoretical S-P time as a guide to define the time window has very little or no effect on the final travel-time observation.

@@

To compute the depth, we select the EW or the NS component with the larger maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the time lag $\tau_{max}$ corresponding to the secondary peak obtained earlier. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064 km, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054 km. We did the same analysis for the eight arrays of the experiment and each of the tremor-location grid points. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

@@

In Table 1, we report the values of the median, the median absolute deviation (MAD), and the Qn estimator of scale for the difference between the depth of the tremor and the low-frequency earthquakes and the depth of the plate boundary, for the McCrory model and for the Preston model. Small negative values of the median correspond to tremor and low-frequency earthquakes located a little bit above the plate boundary. The depth range of the tremor (Qn = 1.3 km) is larger than the depth range of the low-frequency earthquake families from ~\citeA{CHE_2017_JGR,CHE_2017_G3} (Qn = 0.9 km). It is a also larger than the thickness of the flow channel where ~\citeA{SAM_2021} suggest that the LFEs are generated (0.5 to 1.5 km). However, this may be due to the uncertainty on the determination of the tremor depth. The tremor and low-frequency earthquakes are slightly closer to the plate boundary for the Preston model than for the McCrory model. This may be because the P-wave velocity model of ~\citeA{PRE_2003} was used as the initial velocity model by ~\citeA{MER_2020} to compute the full P- and S-wave velocity model that we use to get tremor depth from S minus P times. The Preston P-wave velocity model was also used by ~\citeA{CHE_2017_JGR,CHE_2017_G3} to locate the low-frequency earthquake families. \\

@@

\acknowledgments
The authors would like to thank A. Ghosh for sharing his tremor catalog. We also would like to thank Charles Sammis and an anonymous reviewer whose reviews have helped improve the paper. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS website using network code XG, 2009-2011. Most of the figures were done using GMT ~\cite{WES_1991}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5062659}.
